Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-08-20 Ben_Manuscripts/stochastic_transport/Outline.tex
comments on outline.

\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  % BJC: I've been trying to understand the following justification a bit more. Does it
  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
  % long stochastic simulations that we can't learn from the shorter simulations.
  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
  % putting things in terms of easily interpreted equations.
  % BJC: Maybe it's just a combination of both.
  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab. \\

  One can project long timescale solute behavior by modeling transport as a
  stochastic process.
  \begin{itemize}
    \item Various disciplines study this type of problem in a number of ways.
    \item In the simulation literature, most start by measuring mean squared 
    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
    \item Due to the short time scales most people can feasibly simulate, the MSD 
    does not give a complete picture of what happens long-term, other than hinting
    at types of mechanisms that could lead to the curve's shape.
    \item mean first passage time?
    \item Markov state models are popular with researchers of proteins which have 
    many dynamical states occurring over multiple time scales.
    \item The anomalous diffusion literature explains the shape of MSD curves based
    on rigorous mathematical representations of transport mechanisms. This field is
    heavily used in analysis of single particle tracking experiments.
    \item Finally, the financial literature tackles similar problems from a more 
    general time series perspective. Their primary focus is towards predictions of
    stock market returns and volatility but their methods are widely applicable to
    modeling time series that exhibit a range of behavior.
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
  performed all post-simulation trajectory using python scripts which are available
  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 
  10 \% water by weight. 
  \begin{itemize}
    \item Approximately one third of the water molecules occupy the tail region 
    with the rest near the pore center.
    \item We chose to study the 10 wt \% water system because solutes move 
    significantly faster than in the 5 wt \% system studied previously.
    \item Appropriate stochastic modeling requires that solutes explore 
    as much structural space as possible.  %BJC: better term than structural space?
  \end{itemize}

  We chose to study a subset of 4 of the fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol.
  \begin{itemize} 
    \item In addition to exploring membrane structural space the most, these solutes
    have a relatively diverse set of chemical functionality.   
    \item For each solute we created a separate system and to each system we
    added 6 solutes per pore for a total of 24 solutes.
    \item This number of solutes per pore provides a balance of a low 
    degree of interaction between solutes and sufficient amount of data from
    which to generate statistics on the time scales which we simulate.
    \item Further details on the setup and equilibration of these systems can
    be found in our previous work.\cite{coscia_chemically_2019}
  \end{itemize}

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
  	\begin{enumerate}
  	  \item Trapped in tails
  	  \item Trapped in tails and hydrogen bonding
  	  \item Trapped in tails and associated with sodium
  	  \item Trapped in tails, hydrogen bonding and associated
  	  \item In pores
  	  \item In pores and hydrogen bonding
  	  \item In pores and associated with sodium
  	  \item In pores, hydrogen bonding and associated
  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  \end{itemize}

@@

  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) = exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item The more general family of L\'evy stable distributions allows
    greater flexibility in defining the observed emission distribution PDFs.
    \item In the case that the empirical emission distributions are iid, sequential draws
    from a L\'evy stable PDF defines a L\'evy process. 
    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
    probability distributions if we instead consider the dynamics to be governed by a
    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
    \item OU processes contain temporal dependence but the marginal observation distributions
    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
    \item We will discuss the implications of each.  
  \end{itemize}

@@

  \subsection{Modeling subdiffusion}\label{method:model_sFBM}

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  \begin{itemize}
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while values of
	$\alpha = 1$ and $\alpha > 0$ are characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We analyzed both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
  \end{itemize}

  \noindent Three common mathematical models for modeling anomalous subdiffusion
  processes include continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  \begin{itemize}
    \item FBM is common in crowded, viscoelastic environments where each step comes 
    from a Gaussian distribution but is anti-correlated to its previous 
    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
    \item A CTRW is characterized by a distribution of hop lengths and 
    dwell times, where each each step is characterized by independent random draws from 
    each distribution.\cite{montroll_random_1965,morrin_three_2018}
    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
    \item The processes described above can happen alone or in combination.  	
  \end{itemize}

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

@@

  % BJC: Is it worth showing performance of both types of models? one mode versus two mode?
  % Probably worth showing that 1 state fails
  % BJC: also not sure if there is a better word than mode. I stayed away from 'state' since
  % it's used heavily in the MSM section.
  % BJC: I haven't created the 2 mode model yet, but that'll only take a few hours. I'll
  % do that after I get BCC equilibrations running
  In general, we observe different dynamical behavior when solutes move inside the
  pore versus in the tail region.
  \begin{itemize}
    \item This inspired two models of varying complexity.
    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
    parameter fit to each solute.
    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
    on the solute's radial location.
    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
    pore center and all else are in mode 2, the tail region. 
    \item We determined this cut-off and described how we calculated radial 
    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
  \end{itemize}

@@

  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
  are shown in Figure TBD.
  \begin{itemize}
    \item 2 options for a figure:
    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
  \end{itemize}

  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
  previous work.
  \begin{itemize} 
    \item The extent to which each trapping mechanism influences each solute is
  	depicted graphically in Figure TBD.
    \item Same types of figures from transport paper:
    \item Fraction participating in hydrogen bonds, fraction associated, fraction
    in the tails.
    \item Lifetimes of hbonds and sodium associations?
  \end{itemize}

@@

  % BJC: worth proving these are non-Gaussian? One might argue that they look Gaussian but they are not at all.
  \begin{figure}[!h]
  \includegraphics[width=\textwidth]{emissions_MET.pdf}
  \caption{}\label{fig:emissions_MET}
  \end{figure}

  % BJC: need better or more descriptive way of describing stochastic simulations
  % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
  Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
  observations from the emission distributions yields near linear MSD curves
  with final values that are far higher than those observed in our molecular simulations.
  \begin{itemize}
	% BJC: right number of solute trajectories to simulate for comparison? More tightens the error bars
    \item In the case of methanol, the final MSD value is about 25x higher than that observed in our
    previous transport study (see Figure~\ref{fig:msd_MET}).
    \item The linear behavior of the MSD curve is not consistent with subdiffusion.
  \end{itemize}

  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}

>>>>

%MRS: better to have the first outline shorter to iterate more quickly!

%MRS: better to have a title that described a finding, rather than the
%approach used.  But we may need to wait a bit further until we can decide on a finding.
%MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  % BJC: I've been trying to understand the following justification a bit more. Does it
  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
  % long stochastic simulations that we can't learn from the shorter simulations.
  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
  % putting things in terms of easily interpreted equations.
  % BJC: Maybe it's just a combination of both.

  % MRS: They way to think about it, I think, is that the simplest
  % assumption is the the transport mechanism is simple diffusion;
  % uncorrelated random jumps due to molecular collisions. If you make
  % that assumption, you get MSD linear in time.  So that's IS a
  % stochastic process, but not a very complex one. To make long
  % timescale predictions, we need to increase the detail.  Is that
  % what you are referring to? Not sure if I answered the question . . .

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab. \\

  One can project long timescale solute behavior by modeling transport as a
  stochastic process.
  %MRS: as above, simple diffusion is stochastic, just not very complex.  So we want to add appropriate complexity.
  \begin{itemize}
    %MRS: best talk about these mechanisms in terms of the
    %mathematical models they capture.  But I don't know that it's
    %necessary to review all of them.

    %It may be a better approach to start from the features of the
    %problem (i.e. certain mechanisms) and choose the model (of the
    %existing choices) that is appropriate for those mechanisms.
    %I.e. diagnose first, then choose, rather than just applying a
    %list of models useful in other field's timeseries. Let me know if that makes sense;
    %I think how the methods applied are selected is a key to solve the problem.

    \item Various disciplines study this type of problem in a number of ways.
    \item In the simulation literature, most start by measuring mean squared 
    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
    \item Due to the short time scales most people can feasibly simulate, the MSD 
    does not give a complete picture of what happens long-term, other than hinting
    at types of mechanisms that could lead to the curve's shape.
    %MRS: I'd say that MSD is too simple compared to what is going on mechanistically, but it's fundamentally the same idea.  
    \item mean first passage time?
    \item Markov state models are popular with researchers of proteins which have 
    many dynamical states occurring over multiple time scales.
    \item The anomalous diffusion literature explains the shape of MSD curves based
    on rigorous mathematical representations of transport mechanisms. This field is
    heavily used in analysis of single particle tracking experiments.
    \item Finally, the financial literature tackles similar problems from a more 
    general time series perspective. Their primary focus is towards predictions of
    stock market returns and volatility but their methods are widely applicable to
    modeling time series that exhibit a range of behavior.
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
  performed all post-simulation trajectory using python scripts which are available
  %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 
  10 \% water by weight. 
  \begin{itemize}
    \item Approximately one third of the water molecules occupy the tail region 
    with the rest near the pore center.
    \item We chose to study the 10 wt \% water system because solutes move 
    significantly faster than in the 5 wt \% system studied previously.
    \item Appropriate stochastic modeling requires that solutes explore 
    as much structural space as possible.  %BJC: better term than structural space?
    %MRS: something simpler like ``sample the accessible mechanisms with representative probability''?
  \end{itemize}

  We chose to study a subset of 4 of the fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol.
  \begin{itemize} 
    \item In addition to exploring membrane structural space the most, these solutes
    have a relatively diverse set of chemical functionality.   
    %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
    \item For each solute we created a separate system and to each system we
    added 6 solutes per pore for a total of 24 solutes.
    \item This number of solutes per pore provides a balance of a low 
    degree of interaction between solutes and sufficient amount of data from
    which to generate statistics on the time scales which we simulate.
    \item Further details on the setup and equilibration of these systems can
    be found in our previous work.\cite{coscia_chemically_2019}
  \end{itemize}

@@

  %MRS: probably write it as a 2x4 table.
  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
  	\begin{enumerate}
  	  \item Trapped in tails
  	  \item Trapped in tails and hydrogen bonding
  	  \item Trapped in tails and associated with sodium
  	  \item Trapped in tails, hydrogen bonding and associated
  	  \item In pores
  	  \item In pores and hydrogen bonding
  	  \item In pores and associated with sodium
  	  \item In pores, hydrogen bonding and associated
  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  \end{itemize}

@@

  %MRS: this below sort of goes beyond standard use of MSM's though, right? where everything is usually constant-rate expoential processes? Should be explicitly mentioned.
  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item The more general family of L\'evy stable distributions allows
    greater flexibility in defining the observed emission distribution PDFs.
    \item In the case that the empirical emission distributions are iid, sequential draws
    from a L\'evy stable PDF defines a L\'evy process. 
    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
    probability distributions if we instead consider the dynamics to be governed by a
    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
    \item OU processes contain temporal dependence but the marginal observation distributions
    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
    \item We will discuss the implications of each.  
    %MRS: does the process described above include the motion within the state? That is something I feel that the
    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
  \end{itemize}

@@

  %MRS: you intend this to be a separate model than the above?  If so, make clearer.
  \subsection{Modeling subdiffusion}\label{method:model_sFBM}

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  \begin{itemize}
  %MRS: you would probably want to be clear what the mechanistic reasons for for anomalous diffusion: 
  %want to talk about why, given the mechanisms you would consider. 
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while values of
	$\alpha = 1$ and $\alpha > 0$ are characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We analyzed both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
    %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
  \end{itemize}

  \noindent Three common mathematical models for modeling anomalous subdiffusion
  processes include continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  \begin{itemize}
    \item FBM is common in crowded, viscoelastic environments where each step comes 
    from a Gaussian distribution but is anti-correlated to its previous 
    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
    \item A CTRW is characterized by a distribution of hop lengths and 
    dwell times, where each each step is characterized by independent random draws from 
    each distribution.\cite{montroll_random_1965,morrin_three_2018}
    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
    \item The processes described above can happen alone or in combination.  	
  \end{itemize}
  %MRS: talk about which of these should apply given the data mechanistically, as well as fit.

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  %MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.

  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

@@

  % BJC: Is it worth showing performance of both types of models? one mode versus two mode?
  % Probably worth showing that 1 state fails
  % BJC: also not sure if there is a better word than mode. I stayed away from 'state' since
  % it's used heavily in the MSM section.
  % BJC: I haven't created the 2 mode model yet, but that'll only take a few hours. I'll
  % do that after I get BCC equilibrations running
  In general, we observe different dynamical behavior when solutes move inside the
  pore versus in the tail region.

  %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2.

  \begin{itemize}
    \item This inspired two models of varying complexity.
    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
    parameter fit to each solute.
    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
    on the solute's radial location.
    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
    pore center and all else are in mode 2, the tail region. 
    \item We determined this cut-off and described how we calculated radial 
    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
  \end{itemize}

@@

  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
  are shown in Figure TBD.
  \begin{itemize}
    %MRS: probably option 1.
    \item 2 options for a figure:
    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
  \end{itemize}

  %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
  previous work.
  \begin{itemize} 
    \item The extent to which each trapping mechanism influences each solute is
  	depicted graphically in Figure TBD.
    \item Same types of figures from transport paper:
    \item Fraction participating in hydrogen bonds, fraction associated, fraction
    in the tails.
    \item Lifetimes of hbonds and sodium associations?
  \end{itemize}

@@

  % BJC: worth proving these are non-Gaussian? One might argue that they look Gaussian but they are not at all.
  % MRS: there are some simple statistical tests for Gaussianness you can use.  Also might br good to put the 
  % parameters with the plots, as it's hard to tell how different they may or may not be. 
  \begin{figure}[!h]
  \includegraphics[width=\textwidth]{emissions_MET.pdf}
  \caption{}\label{fig:emissions_MET}
  \end{figure}

  % BJC: need better or more descriptive way of describing stochastic simulations
  % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
  % MRS: could say timeseries simulation?  MD is stochastic as well.
  Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
  observations from the emission distributions yields near linear MSD curves
  with final values that are far higher than those observed in our molecular simulations.
  \begin{itemize}
	% BJC: right number of solute trajectories to simulate for comparison? More tightens the error bars
    \item In the case of methanol, the final MSD value is about 25x higher than that observed in our
    previous transport study (see Figure~\ref{fig:msd_MET}).
    \item The linear behavior of the MSD curve is not consistent with subdiffusion.
  \end{itemize}
  %MRS: so, is there a way we should have been able to tell beforrehand that this approach didn't work that we an explain?
  %or can we show we needed to do this to get the results?
  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}
